Title

### 2023-06-22 main.tex
Cambios

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\tbnote{Jaja sí, va}
\end{itemize}

@@

>>>>

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\tbnote{Jaja sí, va}\\

Finally, we choose a unitary matrix $V$ with the condition that its first
row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
with $\theta$ an arbitrary real number.
That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
since it implies that when $s=0$, the 
state created in \eref{eq:vec}
is
$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
which  corresponds with applying the identity channel.

The choice of such a matrix $V$ can be done at random as follows:
After setting the first row,
construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
using the Gram-Schmidt process.
Then select random complex numbers $r_1, r_2, r_3$ such
that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
define the second row of $V$ to be
$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
Once the first two rows are chosen, use Gram-Schmidt to find two vectors
$\vec{v}_1, \vec{v}_2$ orthogonal to 
them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
selected at random. 
Finally, there is only one choice for the fourth row so that it is 
orthonormal to the first three
and a random phase can be given to it.

@@

\tbnote{Mejor quitar todo lo anterior y dejar esto:}

{\color{purple}
In this work, we found a quantum algorithm for 
simulating Pauli channels in $N$-qubit systems and
generalized it to Pauli dynamical maps.
We observed that the fidelity of 
simulating single-qubit Pauli channels on one of IBM's quantum computers
was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
which was attributed to the current limitations of quantum computers.
Additionally, when working with Pauli dynamical maps,
we determined in theorem \ref{theorem2} the general mathematical conditions
under which a parametrized quantum circuit requires only one single-qubit rotation dependent on the parameter.

Therefore, this work presents another example of the current
exploration into simulating open quantum
systems in quantum computers,
and we observe the big effect that the error of quantum computers have
on these simulations.
On the other hand, the result
of theorem \ref{theorem2}
shows what can be done with the condition of using only one
parametrized rotation and
can be applied to any quantum algorithm that requires parametrized circuits,
such as those used for quantum machine learning.
}
